---
title: "Day 4 Practice"
format: html
editor: visual
execute: 
  warning: false
---

Can add execute: warning: false to get rid of warnings when running code in the yamel

```{r}
library(GGally)
library(skimr)
library(palmerpenguins)
library(tidyverse)
```

## Basic data exploration

Tools for checking out data

-   names: get variables names

-   dim: get data dimensions

-   head: get first n lines (6 by default)

-   tail: get last n lines (6 by default)

-   summary: get basic summary statistics

```{r}
names(penguins)

dim(penguins)

head(penguins)

tail(penguins)

summary(penguins)

# Another summary use skims and gives statistical 
skim(penguins)
## or ::skim??
```

```{r}
## Creating a whole grid of visualizations multiple graphs with respect to multiple variables
# Quick glimpse of values
ggpairs(penguins)

##GGally::ggpairs()
```

## Making more exploratory charts in ggplot2

Histogram: 1 variable chart and then R will count the \# of obersvations in each bin

```{r}
# Fill describes if you have a polygon shape
# Stroke is the outline (fill = '')
# Geom_point has a fill only
ggplot(data = penguins, aes(x = penguins$flipper_length_mm)) + geom_histogram(fill = 'orange',color = "purple" ) + theme_minimal()


ggplot(data = penguins, aes(x = penguins$flipper_length_mm)) + geom_histogram(aes(fill = species)) + theme_minimal()
```

Boxplot

```{r}
ggplot(data = penguins, aes(x = penguins$species, y = penguins$bill_length_mm)) + geom_boxplot(fill = 'yellow', aes(color = island))+theme_dark()

## You can stack plots on top of each other
## alpha will change the transparancy 
## Size based on bill depth 
ggplot(data = penguins, aes(x = penguins$species, y = penguins$bill_length_mm)) + geom_boxplot(fill = 'yellow', aes(color = island))+ geom_jitter(color = "Magenta",alpha = 0.5, aes(size = penguins$bill_depth_mm))+
  theme_dark()

```
